|

### 2021-06-16 appendix/appendix-short.Rmd
first draft

---
title: |
       | Supplementary Materials for "Vigilantism, Institutions, and Culture: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

# Introduction

This appendix contains the `R` code required to replicate the results we
present in "_Vigilantism, Institutions, and Culture: Understanding Attitudes
towards Lynching in Brazil_". This file also includes the descriptive
statistics of our sample, the average marginal component effects (AMCEs) for
our conjoint experiment, and additional subgroup analyses for all three
experiments.

The code below loads the required datasets and the `R` packages we use in our
statistical analyses. It also translates the names of the factor variables from
Portuguese into English.

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
              "janitor", "quanteda", "seededlda", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

# Check for duplicated values
count(get_dupes(df))
```
\normalsize

```{r sample-size, echo=F, warning=F, error=F, message=F, cache=T}
df1 <- df %>% filter(consent == "Agree")
```

We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
five regions of the country (Center-West, North, Northeast, South, and
Southeast). We used quotas for gender and region to ensure that our sample was
similar to the Brazilian population in those characteristics. We also collected
information about whether the subjects had been victimized in the previous 12
months, as well as their opinion of the Brazilian judicial system and the
police forces. They follow in the graphs and tables below.

## Informed Consent

About 98% of the interviewees agreed to participate in the survey experiment.
We excluded the remaining 2% from our analyses.

\footnotesize
```{r consent, warning=F, error=F, cache=T}
df %>%
  group_by(consent) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 2)) %>%
  rename(Consent = consent) %>%
  kbl(., booktabs = TRUE, caption = "Informed Consent") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")

# Remove subjects who did not agree with consent form
df1 <- df %>% filter(consent == "Agree")
```
\normalsize

@@

The gender distribution of our sample is described below. It closely matches
the official data from the [Brazilian Census
Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18320-quantidade-de-homens-e-mulheres.html),
which states that women are 51.8% of the population and men comprise 48.2%.

\footnotesize
```{r gender, warning=F, error=F, cache=T}
df1 %>%
  group_by(gender) %>%
  filter(!is.na(gender)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Gender = gender) %>%
  kbl(., booktabs = TRUE, caption = "Gender") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r age, warning=F, error=F, cache=T, fig.width=6, fig.height=4.3}
tibble(` `    = "Age",
       Median = round(median(df1$age, na.rm = TRUE), 2),
       Mean   = round(mean(df1$age, na.rm = TRUE), 2),
       SD     = round(sd(df1$age, na.rm = TRUE), 2),
       Min    = min(df1$age, na.rm = TRUE),
       Max    = max(df1$age, na.rm = TRUE),
       `NA`   = sum(is.na(df1$age))) %>%
kbl(., booktabs = TRUE, caption = "Age") %>%
row_spec(0, bold = TRUE) %>%
kable_styling(latex_options = "hold_position")

@@

\footnotesize
```{r race, warning=F, error=F, cache=T}
df1 %>%
  rename(Race = race) %>%
  mutate(Race = fct_relevel(Race, "White", "Other", "Rather Not Say", after = Inf)) %>%
  group_by(Race) %>%
  filter(!is.na(Race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r educationtext, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(education) %>%
  filter(!is.na(education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Education = education)
```

@@

\footnotesize
```{r education, warning=F, error=F, cache=T}
df1 %>%
  rename(Education = education) %>%
  mutate(Education = fct_relevel(Education, "Primary School", "Secondary School",
                                 "High School", "College", "Graduate School")) %>%
  group_by(Education) %>%
  filter(!is.na(Education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Education") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r income-text, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(household_income) %>%
  filter(!is.na(household_income)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Household Income` = household_income)
```

@@

\footnotesize
```{r income, warning=F, error=F, cache=T}
df1 %>%
  rename(`Household Income` = household_income) %>%
  mutate(`Household Income` = fct_relevel(`Household Income`, "Up to R$1,000",
                                          "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
                                          "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
                                          "From R$10,001 to R$20,000", "Above R$20,000")) %>%
  group_by(`Household Income`) %>%
  filter(!is.na(`Household Income`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Household Income") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r ideologytext, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(ideology) %>%
  filter(!is.na(ideology)) %>%
  mutate(ideology = fct_relevel(ideology, "Left")) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Ideology = ideology)
```

@@

\footnotesize
```{r ideology, warning=F, error=F, cache=T}
df1 %>%
  rename(Ideology = ideology) %>%
  mutate(Ideology = fct_relevel(Ideology, "Left", "Center-Left", "Center",
                                "Center-Right", "Right")) %>%
  group_by(Ideology) %>%
  filter(!is.na(Ideology)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Political Ideology") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Support for Death Penalty

Below you may find how many respondents support the death penalty.

\footnotesize
```{r death-penalty, warning=F, error=F, cache=T}
df1 %>%
  rename(`Support for Death Penalty` = death_penalty) %>%
  mutate(`Support for Death Penalty` = fct_relevel(`Support for Death Penalty`, "Yes", "No")) %>%
  group_by(`Support for Death Penalty`) %>%
  filter(!is.na(`Support for Death Penalty`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Support for Death Penalty") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Previous Victimization

We asked subjects whether they had been victimized in the previous 12 months,
as crime victims may be more likely to support lynchings. The responses follow
below.

\footnotesize
```{r victimization, warning=F, error=F, cache=T}
df1 %>%
  rename(Victimization = previous_victim_dummy) %>%
  mutate(Victimization = fct_relevel(Victimization, "Yes", "No")) %>%
  group_by(Victimization) %>%
  filter(!is.na(Victimization)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Previous Victimization (12 Months)") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Opinion on the Police

Here we show the results for our question on how respondents see the police
forces.

\footnotesize
```{r police, warning=F, error=F, cache=T}
df1 %>%
  rename(`Opinion on the Police` = views_police) %>%
  mutate(`Opinion on the Police` = fct_relevel(`Opinion on the Police`, "Very Good", "Good",
                                               "Regular", "Bad", "Very Bad")) %>%
  group_by(`Opinion on the Police`) %>%
  filter(!is.na(`Opinion on the Police`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Police") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Opinion on the Judicial System

Lastly, we asked how respondents evaluate their local judiciary. As in the
previous question, subjects could choose among five options, as well as affirm
that they do not have an opinion or decline to answer the question.

\footnotesize
```{r justice, warning=F, error=F, cache=T}
df1 %>%
  rename(`Opinion on the Justice System` = views_justice) %>%
  mutate(`Opinion on the Justice System` = fct_relevel(`Opinion on the Justice System`, "Very Good",
                                                       "Good", "Regular", "Bad", "Very Bad")) %>%
  group_by(`Opinion on the Justice System`) %>%
  filter(!is.na(`Opinion on the Justice System`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Justice System") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

Research shows that police ineffectiveness frequently appears as a strong
predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
result of the weakness of police institutions is that citizens decide to take
criminal matters "into their own hands", thus persecuting and punishing the
criminals by themselves. A recent statistic indicates that the police solves
only 10% of the homicides in Brazil, which lends support to the link between
weak law enforcement and lynchings [@pearson2018latam].

Another possible determinant of lynching support is lack of trust in the
justice system [@godoy2004justice; @smith2019contradictions]. This is often due
to long criminal proceedings, which cause significant anxiety for the victims.
In Brazil, the penal code allows the accused to appeal each decision several
times, so it can take decades before a criminal case is closed
[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
the criminal is put to trial, he/she will be punished in a timely matter. Note
that although the police is technically part of the criminal justice system, we
analyze the two institutions separately in our experiment.

@@

## Main Results

Table \ref{tab:exp01main} summarizes our results. As we see, none of the
treatment effects are statistically significant at conventional levels. This
suggests that institutional factors do not affect lynching support in our
sample.

\footnotesize
```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp01 <- df1 %>%
  mutate(exp01_outcomes = coalesce(exp01_control, exp01_police,
                                   exp01_slow_justice, exp01_small_punishment),
         exp01_any_treat = case_when(!is.na(exp01_control) ~ "0",
                                     !is.na(exp01_police) ~ "1",
                                     !is.na(exp01_slow_justice) ~ "1",
                                     !is.na(exp01_small_punishment) ~ "1",
                                     TRUE ~ NA_character_),
         exp01_police_treat = case_when(!is.na(exp01_control) ~ "0",
                                        !is.na(exp01_police) ~ "1"),
         exp01_slow_justice_treat = case_when(!is.na(exp01_control) ~ "0",
                                              !is.na(exp01_slow_justice) ~ "1"),
         exp01_small_punishment_treat = case_when(!is.na(exp01_control) ~ "0",
                                                  !is.na(exp01_small_punishment) ~ "1"))

# Models
m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)

# Table
stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01main",
          title = "Experiment 01 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

Here we estimate the effect of gender, race, and political ideology on
lynching support. We find that males, blacks, and mixed race individuals are
more likely to endorse lynchings when compared to females and whites,
respectively. Left and center-left voters, in contrast, show lower support for
lynchings when compared to centrists.

\footnotesize
```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp01_group <- df_exp01 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         ideology %in% c("Center", "Center-Left", "Center-Right",
                         "Left", "Right"))

m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_group)
m2 <- lm(exp01_outcomes ~ relevel(race, ref = "White"), data = df_exp01_group)
m3 <- lm(exp01_outcomes ~ relevel(ideology, ref = "Center"), data = df_exp01_group)
m4 <- lm(exp01_outcomes ~ gender + relevel(race, ref = "White") +
         relevel(ideology, ref = "Center"), data = df_exp01_group)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp01baseline",
          title = "Experiment 01 -- Determinants of Baseline Levels of
          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Male", "Asian", "Black", "Mixed Race",
                               "Left", "Center-Left", "Center-Right", "Right"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE)
```
\normalsize

@@

We estimate heterogeneous effects for our experiment using Bayesian Additive
Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
allow users to detect non-linear interactions and are insensitive to the choice
of tuning parameters, so they are well-suited to analyze observational and
experimental data [@green2012modeling]. More specifically, we employ the
`bartCause` package, which is designed to estimate causal inference models.

@@

\footnotesize
```{r exp01-bart01, warning=F, error=F, message=F, cache=T}
df_exp01_het <- df_exp01 %>%
  filter(gender %in% c("Female", "Male")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous"),
         education = fct_relevel(education, "Primary School", "Secondary School",
                                  "High School", "College", "Graduate School"),
         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad"),
         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                     "Bad", "Very Bad"),
         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
                                         "Above R$20,000"),
         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))

df_exp01_police <- df_exp01_het %>%
  mutate(exp01_police_treat = as.numeric(exp01_police_treat)) %>%
  drop_na(exp01_police_treat)

# Gender
summary(bartc(exp01_outcomes, exp01_police_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Age
summary(bartc(exp01_outcomes, exp01_police_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp01_outcomes, exp01_police_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp01_outcomes, exp01_police_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp01_outcomes, exp01_police_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp01_outcomes, exp01_police_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Support for Death Penalty
summary(bartc(exp01_outcomes, exp01_police_treat, death_penalty,
              group.by = death_penalty, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Previous Victimization
df_exp01_police2 <- df_exp01_police %>% drop_na(previous_victim_dummy)
summary(bartc(exp01_outcomes, exp01_police_treat, previous_victim_dummy,
              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_police2,
              n.chains = 5L, seed = 144))

# Opinion on the Police
summary(bartc(exp01_outcomes, exp01_police_treat, views_police,
              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))

# Opinion on the Judicial System
summary(bartc(exp01_outcomes, exp01_police_treat, views_justice,
              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
              n.chains = 5L, seed = 144))
```
\normalsize

@@

\footnotesize
```{r exp01-bart02, warning=F, error=F, message=F, cache=T}
# Remove "Indigenous" and "Other" from `race` as they only
# have 1 observation each. The model cannot be estimated otherwise.
df_exp01_slow_justice <- df_exp01_het %>%
  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
  mutate(exp01_slow_justice_treat = as.numeric(exp01_slow_justice_treat)) %>%
  drop_na(exp01_slow_justice_treat)

# Gender
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, gender,
              group.by = gender, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Age
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, age2,
              group.by = age2, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Race
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, race,
              group.by = race, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Education
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, education,
              group.by = education, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Household Income
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, household_income,
              group.by = household_income, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

# Political Ideology
summary(bartc(exp01_outcomes, exp01_slow_justice_treat, ideology,
              group.by = ideology, group.effects = TRUE, data = df_exp01_slow_justice,
              n.chains = 5L, seed = 144))

>>>>

---
title: |
       | Supplementary Material for "Vigilantism, Institutions, and Honor Culture: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

\appendix

```{r loading, warning=F, message=F, error=F, cache=T, echo=F}
# Install and load required packages
packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
              "janitor", "quanteda", "seededlda", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

df1 <- df %>% filter(consent == "Agree")
```

This appendix contains additional tables and graphs that complement the results
we present in "_Vigilantism, Institutions, and Honor Culture: Understanding
Attitudes towards Lynching in Brazil_". An extended version of this file, which
includes further tests for heterogeneous effects and `R` code, is available at
[_redacted for peer review_]. The repository also contains our pre-analysis
plan and the `php` scripts we used in our conjoint experiment.

We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
five regions of the country (Center-West, North, Northeast, South, and
Southeast).

@@

The gender distribution of our sample closely matches
the official data from the [Brazilian Census
Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18320-quantidade-de-homens-e-mulheres.html),
which states that women are 51.8% of the population and men comprise 48.2%.

\footnotesize
```{r gender, warning=F, error=F, cache=T, echo=F}
df1 %>%
  group_by(gender) %>%
  filter(!is.na(gender)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Gender = gender) %>%
  kbl(., booktabs = TRUE, caption = "Gender") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

\footnotesize
```{r age, warning=F, error=F, cache=T, fig.width=6, fig.height=4.3, echo=F}
tibble(` `    = "Age",
       Median = round(median(df1$age, na.rm = TRUE), 2),
       Mean   = round(mean(df1$age, na.rm = TRUE), 2),
       SD     = round(sd(df1$age, na.rm = TRUE), 2),
       Min    = min(df1$age, na.rm = TRUE),
       Max    = max(df1$age, na.rm = TRUE),
       `NA`   = sum(is.na(df1$age))) %>%
kbl(., booktabs = TRUE, caption = "Age") %>%
row_spec(0, bold = TRUE) %>%
kable_styling(latex_options = "hold_position")

@@

\footnotesize
```{r race, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(Race = race) %>%
  mutate(Race = fct_relevel(Race, "White", "Other", "Rather Not Say", after = Inf)) %>%
  group_by(Race) %>%
  filter(!is.na(Race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r educationtext, echo=F, warning=F, error=F, cache=T, echo=F}
df2 <- df1 %>%
  group_by(education) %>%
  filter(!is.na(education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Education = education)
```

@@

\footnotesize
```{r education, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(Education = education) %>%
  mutate(Education = fct_relevel(Education, "Primary School", "Secondary School",
                                 "High School", "College", "Graduate School")) %>%
  group_by(Education) %>%
  filter(!is.na(Education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Education") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r income-text, echo=F, warning=F, error=F, cache=T, echo=F}
df2 <- df1 %>%
  group_by(household_income) %>%
  filter(!is.na(household_income)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Household Income` = household_income)
```

@@

\footnotesize
```{r income, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(`Household Income` = household_income) %>%
  mutate(`Household Income` = fct_relevel(`Household Income`, "Up to R$1,000",
                                          "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
                                          "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
                                          "From R$10,001 to R$20,000", "Above R$20,000")) %>%
  group_by(`Household Income`) %>%
  filter(!is.na(`Household Income`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Household Income") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

```{r ideologytext, echo=F, warning=F, error=F, cache=T, echo=F}
df2 <- df1 %>%
  group_by(ideology) %>%
  filter(!is.na(ideology)) %>%
  mutate(ideology = fct_relevel(ideology, "Left")) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Ideology = ideology)
```

@@

\footnotesize
```{r ideology, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(Ideology = ideology) %>%
  mutate(Ideology = fct_relevel(Ideology, "Left", "Center-Left", "Center",
                                "Center-Right", "Right")) %>%
  group_by(Ideology) %>%
  filter(!is.na(Ideology)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Political Ideology") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

Research shows that police ineffectiveness frequently appears as a strong
predictor of vigilantism [@garcia2019anger]. The direct result of the weakness
of police institutions is that citizens decide to take criminal matters "into
their own hands", thus persecuting and punishing the criminals by themselves. A
recent statistic indicates that the police solves only 10% of the homicides in
Brazil, which lends support to the link between weak law enforcement and
lynchings [@pearson2018latam].

Another possible determinant of lynching support is lack of trust in the
justice system [@smith2019contradictions]. This is often due to long criminal
proceedings, which cause significant anxiety for the victims. In Brazil, the
penal code allows the accused to appeal each decision several times, so it can
take decades before a criminal case is closed [@sousa2005utilizaccao]. In this
respect, citizens do not believe that, even if the criminal is put to trial,
he/she will be punished in a timely matter. Note that although the police is
technically part of the criminal justice system, we analyze the two
institutions separately in our experiment.

@@

```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis', echo=F}
df_exp01 <- df1 %>%
  mutate(exp01_outcomes = coalesce(exp01_control, exp01_police,
                                   exp01_slow_justice, exp01_small_punishment),
         exp01_any_treat = case_when(!is.na(exp01_control) ~ "0",
                                     !is.na(exp01_police) ~ "1",
                                     !is.na(exp01_slow_justice) ~ "1",
                                     !is.na(exp01_small_punishment) ~ "1",
                                     TRUE ~ NA_character_),
         exp01_police_treat = case_when(!is.na(exp01_control) ~ "0",
                                        !is.na(exp01_police) ~ "1"),
         exp01_slow_justice_treat = case_when(!is.na(exp01_control) ~ "0",
                                              !is.na(exp01_slow_justice) ~ "1"),
         exp01_small_punishment_treat = case_when(!is.na(exp01_control) ~ "0",
                                                  !is.na(exp01_small_punishment) ~ "1"))

m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)
```

@@

We estimate heterogeneous effects for our experiment using Bayesian Additive
Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
allow users to detect non-linear interactions and are insensitive to the choice
of tuning parameters, so they are well-suited to analyze observational and
experimental data [@green2012modeling]. More specifically, we employ the
`bartCause` package, which is designed to estimate causal inference models. The
results are based on 800 posterior samples times 5 chains.

Results vary little in all of our estimations. We find that the personal
characteristics of the respondents have no impact on our main models, which we
report in table 1 in the article. Below we present heterogeneous effects for
the three treatment conditions we included in our experiment. We run one model
for each covariate, namely gender, age, race, education, household income, and
political ideology. To save space, here we only show the average treatment
effect within each group, but the complete results are available in section 3.4
of the extended version of the appendix ([_redacted for peer review_]).

@@

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 1: Police Ineffectiveness}
  \label{tab:exp01het01}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & 0.9729 &  &  & & & \\
  & (2.293) &  &  & & & \\
  Age &  & 1.180 &  & & & \\
  &  & (2.266) &  &  \\
  Race &  &  & 1.0668 & & &  \\
  &  &  & (2.261) & & & \\
  Education &  &  &  & 1.1463 & & \\
  &  &  &  & (2.277) & & \\
  Household Income &  &  &  & & 1.1459 & \\
  &  &  &  & & (2.290) & \\
  Political Ideology &  &  &  & & & 1.3693 \\
  &  &  &  & & & (2.225) \\
 N & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}
\normalsize

@@

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 2: Criminal Justice
  Ineffectiveness}
  \label{tab:exp01het02}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & -0.0752 &  &  & & & \\
  & (2.372) &  &  & & & \\
  Age &  & -0.2788 &  & & & \\
  &  & (2.379) &  &  \\
  Race &  &  & NA & & &  \\
  &  &  & (NA) & & & \\
  Education &  &  &  & 0.2204 & & \\
  &  &  &  & (2.347) & & \\
  Household Income &  &  &  & & -0.0295 & \\
  &  &  &  & & (2.331) & \\
  Political Ideology &  &  &  & & & -0.0936 \\
  &  &  &  & & & (2.339) \\
 N & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{\textbf{Note}: There are no estimates for race because some
groups have no observations.}
\end{tabular}
\end{table}
\normalsize
